### 2019-08-14 Writeup/Thesis/pages/design.tex
Changes; - Added frame for conference paper - Moved both projects into a shared folder
Changes; - More corrections made

This chapter will discuss and overview of the proposed designs for elements required to answer the research questions. Alternative solutions are explained when relevant alongside a justification of design choices.

@@

The attack on Trustwords involves generating "near-collision" keys. 
This will attempt to provide the base to answer Research Questions \ref{goal:numberOfTrustwords}, \ref{goal:complexity} and \ref{goal:hardwareRequired}.

Near-collision keys are keys that are deemed a match by the phonetic similarity metric (More on this aspect in the following sections). A similarity metric is an algorithm designed to determine if two words are phonetically a match. For example, the words "THEIR" and "THERE" will be a match whereas the words "DARK" and "PRINCIPLE" are not phonetically matching.

As each combined key in Trustwords is an exclusive-or of both sides' public key (Figure \ref{fig:xor_trustwords} shows this process) the attack is designed to target a single pair of users and will require recomputation for every attack target. This will be considered when discussing the attack feasibility. Each pair is also split into an "Uncontrolled" or "Controlled" key. Uncontrolled is the receiver of the communication, and, thus, we cannot control their key. The Controlled key is the one we are attempting to impersonate, and it is assumed that we have the ability to replace the Controlled key with our malicious option. These descriptions will be the terminology used throughout the paper. However, it should also be considered that the uncontrolled and controlled can be swapped around with the ability to compute both directions. Thus, resulting in the possibility to intercept both directions of communication. This, however, will require performing the attack separately for both directions.

@@

When attacking the respective similarity metric will be used to compute a list of possibilities for each position in the combined fingerprint.

Figure \ref{fig:nearMatch} shows the process of generating a subsection of the combinations. A list of each words' matches is generated, followed by the generation of the total number of near-collision keys.

@@

    \verb|CHOKE                          |
    \\
    \verb|COKE                           |
    \\
    \begin{BVerbatim}[commandchars=\\\{\}]
        \centering
\textbf{ SMOKE BLUSHING FRIGHTENING HAND}
    \end{BVerbatim}
    \caption{Visualization of the generation of near matches}
    \label{fig:nearMatch}
\end{figure}

In order to generate an actual list of fingerprints to search for, the near-collision words are converted back into hexadecimal and XORed with the uncontrolled key. This provides the impersonated key that will produce the desired Trustwords. Completing this for all of the near-collision permutations will produce a list of fingerprints that can be inserted into a tool designed to hash keys and search for targets. This aspect of using a large list to search for keys massively reduces the complexity of the search.

@@

\section{Similarity metrics}
\label{sec:metrics}
One of the first requirements for the attack is quantifying "phonetic similarity." This section is looking to provide an answer for Research Question \ref{goal:phoneticSimilarity}. There are many algorithms currently available to provide this functionality. This section will describe algorithms alongside the reasons they were selected for assessment later in the project.

\subsection{Soundex}
One of the earliest examples of a phonetic algorithm is known as Soundex. It is one of the most famous algorithm due in part to its implementation into major database clients like MySQL\cite{mysql_soundex}, Oracle\cite{moved_2005} and PostgreSQL\cite{postgresql}. Originally designed for indexing names by phonetics alongside spelling mistakes due to transpositions in letters. Therefore, due to it being based on the phonetic features, it is highly suitable for this project's use-case.

Soundex produces a four digit code for each word assessed.
The first letter of the word is retained alongside the removal of all of a, e, i, o, u, y, h and w. The remaining letters are then mapped to numbers. These mappings are displayed in Figure \ref{fig:soundexMap}.

@@

Due to the fixed length and limited digit set the initial concerns from this design is the limited number of combinations. There are a total of 5616 codes due to 26 initial letters and three digits of 6 values ($26 * 6^3$).
The limited combinations will result in matches of a limited quality.

@@

\begin{enumerate}
    \item \textbf{Dependency on the first letter:} Soundex cannot match words together if their first letters are different, meaning for example the words "KORBIN" and "CORBIN" will never be matched.

@@

    \item \textbf{Poor precision.} Due to the previously discussed point of a small code space. \cite{patman2001soundex} re-iterates this point but in the context of name matching where Soundex's poor performance was demonstrated. Soundex only gained and overall accuracy of 36.37\% when matching names within a provided database.
\end{enumerate}

However, even with Soundex's fallbacks its algorithmic simplicity and popularity allows it to still remain relevant in this application.

\subsection{NYSIIS}
The New York State Identification and Intelligence System (NYSIIS) phonetic code was created for use matching the phonetics of American names. It was created due to the presence of hispanic names in the American based databases (this was an aspect Soundex was known to have low accuracy with). However, due to it having embedded rules to handle word phonetics it would, again be applicable in this application.

It also allows for variable length codes and, thus, allows the applicability of the application to increase due to it not confronting the limited code issue of Soundex. It was in use right up the end of 1998 within various US Government departments. Due to NYSIIS's aforementioned use in a professional setting alongside its high occurrence in literature, it was deemed suitable as one of the selected similarity metrics.

@@

\subsection{Levenshtein Distance}
Levenshtein distance is a string metric designed to measure the 'distance' between two strings. It is simply the number of single-character edits (insertions, deletions or substitutions) required to reach the other string. Edit distance is not technically designed as a phonetic algorithm, but due to similar-sounding words often being spelt in similar ways\cite{hettiarachchi2012sparcl} Levenshtien distance was deemed another suitable metric. Levenshtein is also the most algorithmically simplistic of all the options, this further contributes to its appeal as a chosen metric.

An example distance between \verb|trace| and \verb|place| would be the substitutions of the first to letters, from \verb|tr| to \verb|pl| meaning the two strings have a Levenshtein distance of 2.

\subsection{Phonetic Vectors}
Phonetic Vectors is the unique addition to the chosen set. Created by Allison Parrish in 2017\cite{parrish2017poetic}, Phonetic vectors is as the name suggests the vectorization of a words phonetics. This phonetical representation in vector space.

Phonetic features are used in this work as a way to compare the similarity of a words phonemes. Phonemes are the phonetic elements that construct a word. For example the word "RING" translated into the phonemes \verb|/R IH NG/|.

Extensive prior work has gone into producing models of features that map to phonemes \cite{chomsky1968sound}\cite{ladefoged1969measurement}\cite{bradlow2010perceptual}. Features, therefore, are an attempt at mapping the varying and inconsistent rules around pronunciation of the English language. The vectors were created using lists phonemes from the CMU Pronouncing Dictionary and mapping them to possible features.

@@

This metric allows for a unique set of actions to be performed on the phonetic output. Not only does this metric allow the user to measure \textit{dissimilarity} (opposed to the similar-or-not method of the alternatives) the continuous nature of the value allows mathematical operations to be performed on the output. An example shown in \cite{parrish2017poetic} was the addition of word vectors.

@@

The ability to perform operations and measure dissimilarity allows for a plethora of applications. One possible application of note would be the creation of a wordlist where the phonetic difference (vector distance) is maximized. This, if the vector mappings are an accurate representation could allow a creation of a phonetically distinctive wordlist. These unique aspects contributes to inclusion of this metric in the set.

@@

\subsection{Match Rating Approach}
Matching Rating Approach (MRA) is another algorithm designed to match names within a database, therefore, its operation can be grouped with that of NYSIIS and Soundex. MRA was discarded as an option. This is because of the lack of known utilization in any substantial real world use-cases alongside its similarity to more well established algorithms of Soundex and NYSIIS.

Further work could include the comparison of this algorithm  to similar alternatives in phonetically matching of words to quantify performance. This will be discussed further in the evaluative sections of the report.

\subsection{Caverphone}
Another notable alternative solution is that of Caverphone that was designed in New Zealand. Caverphone as is the case with the vast majority of phonetic algorithms was designed for use with name matching. Caverphone was not chosen to similar reasons to that of MRA alongside its optimization for the New Zealand accent. Therefore, the low level of utilization alongside the unique design features that suggests it may not be suited for this application. This has, however, not be assessed empirically and thus would be a candidate for further work.

@@

\section{Design of GreenOnion}
\label{sec:greenDesign}
To answer Research Questions \ref{goal:complexity} and \ref{goal:hardwareRequired} fully, it is necessary to implement an actual code base that will be used to generate actual keys.

Inspiration of the design of this tool was taken from a tool called Scallion\footnote{\url{https://github.com/lachesis/scallion}}. Scallion was designed by Richard Klafter and Eric Swanson and used to demonstrate that 32-bit PGP key ids were insufficient. Keeping with the onion-based theme the proposed tool is known as GreenOnion and is a re-write of the tools structure in C++. This language was chosen due to the well understood efficiency benefits. The proposed tool differs from Scallion most notably in its ability to concurrently search for a large number of keys, GreenOnion improves on this substantially. More implementation and experimental details will be discussed in later chapters.

The tool should take two keys as parameters (Uncontrolled/Controlled) and a chosen similarity metric and produce a list of target keys fingerprints. This list is then used as a search criteria when hashing a checking a large number of keys. In order to utilise the high parallel nature of the GPU to compute the hash of a large number of keys the tool will utilise a GPGPU (General-purpose computing on graphics processing units) framework. The chosen framework was OpenCL due to its support for the chosen language (C++) and platform (Linux). OpenCL allows the creation of code chunks referred to as "kernels" to be executed concurrently, this will provide a massive speed increase compare to the sequential nature of the CPU. Technical details will be explained further in Chapter \ref{cha:Implementation}.

\section{Experiment Design}
In order to answer some of the research questions empirical evidence is required and, thus, experiments are required. In this section the designs and considerations of the chosen experiments will be discussed.

\subsection{Metric performance}
\label{exp:metric}
In order to answer Research Question \ref{goal:bestMetrics} and reduce the number of metrics to assess in the later rounds, the performance of similarity metrics required comparison. The thinning out of metrics is required due to limited resources and, therefore, possible further work could involve repeating this work with a much more varied selection of metrics. As explained in a previous section (See Section \ref{sec:metrics}) the chosen metrics up for assessment are Soundex, Metaphone, NYSIIS, Levenshtein and Phonetic vectors.

@@

In the case of Levenshtein values of similarity are discrete due to it being the number of single character edits. Therefore, this requires less deliberation. Match size was used as a way to decide on a cut-off point.

@@

As it can be seen from Table \ref{tab:matchSize} the number of matches for L2 is massively larger than all metrics excluding Soundex. As the issues with Soundex have been discussed in previous sections (See Section \ref{sec:soundexIssues}) it can be excluded as an abnormality in this context. Therefore, due to the excessively high value for a L2, L1 was chosen as the Levenshtein cap for defining a match.

Match size was also used to define the cap for the phonetic vectors. This is less distinct that that of Levenshtein due to the continuous nature of the distance between two vectors, however the complexity was reduced by limiting it to increments of 0.5.

@@

Table \ref{tab:vectorMatchSize} contains the match size comparison for Phonetic vectors distance. Distance 4.5 was chosen as the suitable size due to the total matches fitting well within the other metrics. Distance 4.0 was the other alternative, this was discarded due to its small size. Any metric with a number of matches below 100,000 results in an inadequate number of possible near-collision keys later in the process, a lower number of matches may imply better quality but a balance is required between computational cost and attack quality. This will be discussed in more detail in later chapters.

@@

\subsubsection{Comparisons}
Each participant is asked to rate the similarity of a match on a scale of 1 to 5. Figure \ref{fig:phoneticMatch} shows an example match and the connected scale. Users will complete five of these comparisons per metric.

@@

The experiment randomizes the order of these comparisons per session alongside a complete refreshing of matches once per submission. This makes sure selections from the samples are fair and consistent as each user will have a different selection of matches.

\subsubsection{Quality control}
\label{sec:exp1_qualitycontrol}
As the study was being outsourced to Amazon's Mechanical Turk the requirement to check the quality of results is important. Therefore, a couple of additions were provided to check a result's validity.

The first was the addition of five "Random matches" questions. These are matches consisting of two random words selected from the dictionary. Therefore, the expected average rating of these words should be close to 1. This allows a simple check to see if the user is providing valid results. If their average is too high, the results will be discarded.

@@

Alongside this, was the addition of two questions comparing exactly the same word. As both words are the same the result should always be a full 5/5 rating, any results without a full rating will be discarded. Figure \ref{fig:exactMatch} contains one example of the attention questions used to filter inaccurate results.

The final check to ensure the validity of results is a check for native English fluency. Having non-native English speakers complete the 
experiment has the possibility to introduce inconsistencies into the 
data and, therefore, needs to remain controlled. To achieve this a 
preliminary MTurk study will be run to ask users for their perceived 
English fluency on a scale of 1 (Basic Understanding) to 5 (Native). 
Workers with an answer of 5 will be provided with a 
Qualification\footnote{\url{https://blog.mturk.com/tutorial-understanding-requirements-and-qualifications-99a26069fba2}} 
that tags them as defining themselves as native speakers. This is then 
added as a prerequisite when running the experiment. This will insure 
only fully native speakers are being assessed. The possibility of the 
worker falsely stating their level of fluency has also been considered. 
However, as the worker does not know the purpose for this initial study,
thereby providing inaccurate results has no real valid motive for the 
worker.

@@

The first consideration is the way the words are compared. Due to the channel of authentication being phone based the comparison of words will be a mixture of auditory and textual. This is because a user needs to match a words sound to the one displayed on their device. In the case of this experiment the users are asked to compare the sound of two word that are visually displayed to them.

This visual aspect is the first point of contact between the participant and the question, followed by mental comparison of the phonetics of the word. Therefore, this initial visual contact has the potential to bias the results of the study. Levenshtein has the potential to be most affected by this due to the matches never being more than one character different, therefore, resulting in very similar looking words. The alternative method of running this experiment is to get users to compare audio samples of words, this will force the user to compare just the phonetics of the words and not be influenced by the visual aspects of the pair. This, however, adds a substantial cost onto the operation of the study. Due to the aforementioned lack of resources the chosen design was decided as most feasible as it is a balance between cost and accuracy. Further work, therefore, could improve by producing more conclusive results on the performance of the metrics by implementing the more accurate but costly alternative.

Another consideration is the demographics of people accessible on Mechanical Turk. A comprehensive and still active survey run by D Difallah \textit{et al.} \cite{difallah2018demographics} shows that MTurk workers are younger and have a larger household income than that of the US population. This has to be taken into consideration when interpreting the results because it will inherently introduce a bias. This is due to the assumptions that an increase in age provides a better understanding of more obscure words, and, therefore, a better representation of the metrics performance over the entire dictionary.

@@

The final experiment required to answer the Research Question \ref{goal:attackPercentage} will simulate attacks on participants. The user will be presented with the same design as presented in the \pep Android application (See Section \ref{sec:pep}).

@@

Figure \ref{fig:expID} shows the design of the experiments front end. As can be seen by comparing it to Figure \ref{fig:trustwords} it has been designed to be a close as possible to the actual application. Users will click the blue button to simulate the authentication ceremony over the phone. A text-to-speech system will then read a set of words and the user should accept if they match and decline if they don't.

@@

Due to the scarcity of attacks in a real-world setting users will are often complacent about their occurrence. Therefore, in this experiment attacks only occur 30\% of the time. This is a much higher value than in a real-world setting, but it is a balance between resources and realistic design. Alongside, this the first 5 trials of a new experiment will always be benign. This is to ensure users are lulled into a level of complacency regarding the possibility for an attack.

Certain keys have higher levels of near-collision possibilities than others due to how certain words are deemed similar by the chosen metric. Therefore, this presents the possibility to have keys with a very low number of similar matches. The distribution of these keys will be explained further in Chapter \ref{cha:Experiments}. Therefore, if random sets of words were chosen with no restraints there are attacks presented to the user that in a real setting would be infeasible as they are close to a $2^{64}$ attack (4 Words * 16-bits). Therefore, the experiment will sample from a list of "vulnerable" keys. These are keys that have a number of combinations that allow an attack in a certain timeframe. Furthermore, certain levels of attacks are also simulated. Below are the list of possible attacks:

@@

The start and ends were chosen as the highest priority words to keep static. This is due to research highlighting on the common habit of users to only check the start and end of a checksum. \cite{cherubini2018towards} shows this by measuring user eye movement and displaying it as a heat map.

@@

Figure \ref{fig:heatMap} shows the results of a eye tracking experiment where the user failed to detect a mismatching digest. As it can be clearly seen the users never compared the center of the digest.

>>>>

This chapter discusses an overview of the proposed designs for elements required to answer the research questions. Alternative solutions are explained when relevant alongside a justification of design choices.

@@

The attack on Trustwords involves generating "near-collision" keys. 
This attempts to provide the base to answer Research Questions \ref{goal:numberOfTrustwords}, \ref{goal:complexity} and \ref{goal:hardwareRequired}.

Near-collision keys are keys that are deemed a match by the phonetic similarity metric (More on this aspect in the following sections). A similarity metric is an algorithm designed to determine if two words are phonetically a match. For example, the words "THEIR" and "THERE" is a match, whereas the words "DARK" and "PRINCIPLE" are not phonetically matching.

As each combined key in Trustwords is an exclusive-or of both sides' public-key (Figure \ref{fig:xor_trustwords} shows this process) the attack is designed to target a single pair of users and requires recomputation for every attack target. This aspect is considered when discussing the attack feasibility. Each pair is split into an "Uncontrolled" or "Controlled" key. Uncontrolled is the receiver of the communication, and, thus, the key cannot be altered. The Controlled key is the one we are attempting to impersonate. It is assumed that there is the ability to replace the Controlled key with the malicious option. These descriptions are the terminology used throughout the paper. However, the uncontrolled and controlled keys can be swapped around with the ability to compute both directions. Thus, resulting in the possibility to intercept both directions of communication. This, however, requires performing the attack separately for both directions.

@@

When attacking a similarity metric is used to compute a list of possibilities for each position in the target fingerprint.

Figure \ref{fig:nearMatch} shows the process of generating a subsection of the combinations. A list of each words' matches is generated and combined to create the comprehensive list of near-collision keys.

@@

    \verb|CHOKE                          |
    \\
    \verb|COKE                           |
    \\
    \begin{BVerbatim}[commandchars=\\\{\}]
        \centering
\textbf{ SMOKE BLUSHING FRIGHTENING HAND}
    \end{BVerbatim}
    \caption{Visualisation of the generation of near matches}
    \label{fig:nearMatch}
\end{figure}

Completing these steps produces a list of fingerprints that can be inserted into a tool designed to hash a large number of keys and search for matches. This aspect of using a extensive list to search for keys massively reduces the complexity of the search.

@@

\section{Similarity metrics}
\label{sec:metrics}
One of the first requirements for the attack is quantifying "phonetic similarity." This section is looking to provide an answer for Research Question \ref{goal:phoneticSimilarity}. There are many algorithms currently available to provide this functionality. This section describes the algorithms alongside the reasons they were selected for assessment later in the project.

\subsection{Soundex}
One of the earliest examples of a phonetic algorithm is known as Soundex. It is one of the most famous algorithms due in part to its implementation into major database clients like MySQL\cite{mysql_soundex}, Oracle\cite{moved_2005} and PostgreSQL\cite{postgresql}. Initially designed for indexing names by phonetics alongside spelling mistakes due to transpositions in letters. Therefore, due to it being based on the phonetic features, it is highly suitable for this project's use-case.

Soundex produces a four-digit code for each word assessed.
The first letter of the word is retained alongside the removal of all of a, e, i, o, u, y, h and w. The remaining letters are then mapped to numbers. These mappings are displayed in Figure \ref{fig:soundexMap}.

@@

Due to the fixed length and limited digit set the initial concerns from this design is the limited number of combinations. There are a total of 5616 codes due to 26 initial letters and three digits of 6 values ($26 * 6^3$).
The limited combinations result in matches of limited quality.

@@

\begin{enumerate}
    \item \textbf{Dependency on the first letter:} Soundex cannot match words together if their first letters are different, meaning, for example, the words "KORBIN" and "CORBIN" are considered non-matching.

@@

    \item \textbf{Poor precision.} Due to the previously discussed point of a limited code space. \cite{patman2001soundex} re-iterates this point, but in the context of name matching where Soundex's poor performance was demonstrated. Soundex only gained and overall accuracy of 36.37\% when matching names within a provided database.
\end{enumerate}

However, even with Soundex's issues, it's algorithmic simplicity and popularity allows it to remain relevant in this application.

\subsection{NYSIIS}
The New York State Identification and Intelligence System (NYSIIS) phonetic code was created for use matching the phonetics of American names. The motivation for it's inception was mostly due to the presence of Hispanic names in the American based databases (this was an aspect Soundex was known to have low accuracy with). However, due to it having embedded rules to handle word phonetics, it would again be applicable in this application.

It also allows for variable-length codes and, thus, allows the applicability of the application to increase due to it not confronting the limited code issue of Soundex. It was in use right up util the end of 1998 within various US Government departments. Due to NYSIIS's aforementioned use in a professional setting alongside its high occurrence in literature, it was deemed suitable as one of the selected similarity metrics.

@@

\subsection{Levenshtein Distance}
Levenshtein distance is a string metric designed to measure the 'distance' between two strings. It is merely the number of single-character edits (insertions, deletions or substitutions) required to reach the other string. Edit distance is not technically designed as a phonetic algorithm, but due to similar-sounding words often being spelt in similar ways\cite{hettiarachchi2012sparcl}. Alongside this, Levenshtein is also the most algorithmically simplistic of all the considered options. These aspects contributed to Levenshtein's inclusion.

An example distance between \verb|trace| and \verb|place| would be the substitutions of the first to letters, from \verb|tr| to \verb|pl|, meaning the two strings have a Levenshtein distance of 2.

\subsection{Phonetic Vectors}
Phonetic Vectors is a unique addition to the chosen set. Created by Allison Parrish in 2017\cite{parrish2017poetic}, Phonetic vectors is as the name suggests the vectorisation of the phonetics of a word.

Phonetic features are used in this work as a way to compare the similarity of phonemes. Phonemes are the phonetic elements that construct a word. For example, the word "RING" translated into the phonemes \verb|/R IH NG/|.

Extensive prior work has gone into producing models of features that map to phonemes \cite{chomsky1968sound}\cite{ladefoged1969measurement}\cite{bradlow2010perceptual}. Features, therefore, are an attempt at mapping the varying and inconsistent rules around the pronunciation of the English language. The vectors were created using lists phonemes from the CMU Pronouncing Dictionary and mapping them to possible features.

@@

This metric allows for a unique set of actions to be performed on the phonetic output. Not only does this metric allow the user to measure \textit{dissimilarity} (as opposed to the similar-or-not method of the alternatives) the continuous nature of the value allows mathematical operations to be performed on the output. An example shown in \cite{parrish2017poetic} was the addition of word vectors.

@@

The ability to perform operations and measure dissimilarity allows for a plethora of applications. One possible application of note would be the creation of a wordlist where the phonetic difference (vector distance) is maximised. This application, if the vector mappings are an accurate representation, could allow the creation of a phonetically distinctive wordlist. These unique aspects contribute to the inclusion of this metric in the set.

@@

\subsection{Match Rating Approach}
Matching Rating Approach (MRA) is another algorithm designed to match names within a database; therefore, its operation can be grouped with that of NYSIIS and Soundex. MRA was discarded as an option. This removal of this metric is due to the lack of known utilisation in any substantial real-world use-cases alongside its similarity to  more established algorithms like Soundex and NYSIIS.

Further work could compare this algorithm to similar alternatives in phonetically matching of words to quantify performance. This further work is discussed in the evaluative sections of the report.

\subsection{Caverphone}
Another notable alternative solution is that of Caverphone that was designed in New Zealand. Caverphone, as is the case with the vast majority of phonetic algorithms, was designed for use with name matching. Caverphone was not chosen to similar reasons to that of MRA alongside its optimisation for the New Zealand dialect. Therefore, the low level of utilisation alongside the unique design features contributed to its exclusion. However, this has not been assessed empirically and thus would be a candidate for further work.

@@

\section{Design of GreenOnion}
\label{sec:greenDesign}
In order to answer Research Questions \ref{goal:complexity} and \ref{goal:hardwareRequired} fully, it is necessary to implement an actual tool to generate actual keys.

The inspiration for the design of this tool was taken from a tool called Scallion\footnote{\url{https://github.com/lachesis/scallion}}. Scallion was designed by Richard Klafter and Eric Swanson and was used to demonstrate that 32-bit PGP key IDs were insufficient. To keep with the onion-based theme, the proposed tool is known as GreenOnion and is a re-write of Scallion in C++. This language was chosen due to the well-understood efficiency benefits. The proposed tool differs from Scallion, most notably in its ability to concurrently search for a large number of keys, GreenOnion improves on this substantially. More implementation and experimental details are discussed in later chapters.

The tool should take two keys as parameters (Uncontrolled/Controlled) and a chosen similarity metric and produce a list of target keys fingerprints. This list is then used as a search criterion when searching for keys. To utilise the parallel nature of the GPU to compute the hash of a large number of keys, the tool utilises a GPGPU (General-purpose computing on graphics processing units) framework. The chosen framework was OpenCL due to its support for the chosen language (C++) and platform (Linux). OpenCL allows the creation of code chunks referred to as "kernels" to be executed concurrently, this provides a massive speed increase compared to the sequential nature of the CPU. Technical details are explained further in Chapter \ref{cha:Implementation}.

\section{Experiment Design}
To answer some of the research questions, empirical evidence is required and, thus, experiments are required. In this section, the designs and considerations of the chosen experiments are discussed.

\subsection{Metric performance}
\label{exp:metric}
This section answers Research Question \ref{goal:bestMetrics}. To reduce the number of metrics to assess in the later rounds, the performance of similarity metrics required comparison. The thinning out of metrics is required due to limited resources. Therefore, possible further work could involve repeating this work with a much more varied selection of metrics. As explained in a previous section (See Section \ref{sec:metrics}) the chosen metrics up for assessment are Soundex, Metaphone, NYSIIS, Levenshtein and Phonetic vectors.

@@

In the case of Levenshtein values of similarity are discrete due to it being the number of single-character edits. Therefore, this requires less deliberation. Match size was used as a way to decide on a cut-off point.

@@

As it can be seen from Table \ref{tab:matchSize}, the number of matches for L2 is more significant than all metrics excluding Soundex. As the issues with Soundex have been discussed in previous sections (See Section \ref{sec:soundexIssues}) it can be excluded as an abnormality in this context. Therefore, due to the excessively high value for a L2, L1 was chosen as the Levenshtein cap for defining a match.

Match size was also used to define the cap for the phonetic vectors. The decision is less apparent that that of Levenshtein due to the continuous nature of the distance between two vectors. However, the complexity was reduced by limiting it to increments of 0.5.

@@

Table \ref{tab:vectorMatchSize} contains the match size comparison for Phonetic vectors distance. Distance 4.5 was chosen as a suitable size due to the total matches fitting well within the other metrics. Distance 4.0 was the other alternative; this was discarded due to its small size. Any metric with a number of matches below 100,000 results in an inadequate number of possible near-collision keys later in the process, a lower number of matches may imply better quality, but a balance is required between computational cost and attack quality. This is discussed in more detail in later chapters.

@@

\subsubsection{Comparisons}
Each participant is asked to rate the similarity of a match on a scale of 1 to 5. Figure \ref{fig:phoneticMatch} shows an example match and the connected scale. Users are provided with five of these comparisons per metric.

@@

The experiment randomises the order of these comparisons per session alongside a complete refreshing of matches once per submission. This design makes sure selections from the samples are fair and consistent as each user has a different selection of matches.

\subsubsection{Quality control}
\label{sec:exp1_qualitycontrol}
As the study was being outsourced to Amazon's Mechanical Turk, the requirement to check the quality of results is essential. Therefore, a couple of additions were provided to check a result's validity.

The first was the addition of five "Random matches" questions. These are matches consisting of two random words selected from the dictionary. Therefore, the expected average rating of these words should be close to one. This design allows for a simple check for valid results. If their average is too high, their results are discarded.

@@

Alongside this, was the addition of two questions comparing precisely the same word. As both words are the same, the result should always be a full 5/5 rating, any results without a full rating are discarded. Figure \ref{fig:exactMatch} contains one example of the attention questions used to filter inaccurate results.

The final check to ensure the validity of results is a check for native English fluency. Having non-native English speakers complete the 
experiment can introduce inconsistencies into the 
data and, therefore, needs to remain controlled. To achieve this, a preliminary MTurk study has been created to ask users for their perceived 
English fluency on a scale of 1 (Basic Understanding) to 5 (Native). 
Workers with an answer of 5 are provided with a 
Qualification\footnote{\url{https://blog.mturk.com/tutorial-understanding-requirements-and-qualifications-99a26069fba2}} 
that tags them as defining themselves as native speakers. This qualification is then 
added as a prerequisite when running the experiment. This prerequisite ensures 
only fully native speakers are being assessed. The possibility of the 
worker falsely stating their level of fluency has also been considered. 
However, as the worker does not know the purpose of this initial study,
thereby providing inaccurate results has no real valid motive for the 
worker.

@@

The first consideration is the way the words are compared. Due to the channel of authentication being phone-based, the comparison of words is a mixture of auditory and textual. This mixture is because a user needs to match a words sound to the one displayed on their device. This experiment asks users to compare the sound of two words that are visually displayed to them. This visual aspect is the first point of contact between the participant and the question, followed by a mental comparison of the phonetics of the word. Therefore, this initial visual contact has the potential to bias the results of the study. Levenshtein has the potential to be most affected by this due to the matches never being more than one character different, therefore, resulting in very similar-looking words. The alternative method of running this experiment is to get users to compare audio samples of words; this forces the user to compare just the phonetics of the words and not be influenced by the visual aspects of the pair. However, this adds a substantial cost to the operation of the study. Due to the aforementioned lack of resources, the chosen design was decided as most feasible as it is a balance between cost and accuracy. Further work, therefore, could improve by producing more conclusive results on the performance of the metrics by implementing the more accurate but costly alternative.

Another consideration is the demographics of people accessible on Mechanical Turk. A comprehensive and still active survey run by D Difallah \textit{et al.} \cite{difallah2018demographics} shows that MTurk workers are younger and have a more substantial household income than that of the US population. This deviation has to be taken into consideration when interpreting the results because it has to potential to introduce a bias.

@@

\todo{Include explination into how audio is generated}

The final experiment required to answer Research Question \ref{goal:attackPercentage} requires the simulation attacks on participants. The user is presented with the same design as the \pep Android application (See Section \ref{sec:pep}).

@@

Figure \ref{fig:expID} shows the design of the experiments front end. As can be seen by comparing it to Figure \ref{fig:trustwords}, it has been designed to be as close as possible to the actual application. The blue button is clicked to simulate the authentication ceremony over the phone. A text-to-speech system then read a set of words and the user should accept if they match and decline if they don't.

@@

Due to the scarcity of attacks in a real-world setting users are often complacent about their occurrence. Therefore, in this experiment, attacks only occur 30\% of the time. This occurrence is a much higher value than in a real-world setting, but it is a balance between resources and realistic design. Alongside, this the first 5 trials of a new experiment is always benign. This inclusion is to ensure users are lulled into a level of complacency regarding the possibility of an attack.

Certain keys have higher levels of near-collision possibilities than others due to how certain words are deemed similar by the chosen metric. Therefore, this presents the possibility to have keys with a very low number of similar matches. The distribution of these keys is explained further in Chapter \ref{cha:Experiments}. Therefore, if random sets of words are chosen with no restraints, there are attacks presented to the user that in a real setting would be infeasible as they are close to a $2^{64}$ attack (4 Words * 16-bits). Therefore, the experiment is designed to sample from a list of "vulnerable" keys. These are keys that have a number of combinations that allow an attack in a specified timeframe.

Furthermore, certain levels of attacks are also simulated. Below is the list of possible attacks:

@@

The start and ends were chosen as the highest priority words to keep static. This design choice is due to research highlighting on the common habit of users only to check the start and end of a checksum. \cite{cherubini2018towards} shows this by measuring user eye movement and displaying it as a heat map.

@@

Figure \ref{fig:heatMap} shows the results of an eye-tracking experiment where the user failed to detect a mismatching digest. As it can be seen, the users never compared the centre of the digest.

### 2019-08-14 Writeup/Thesis/pages/evaluation.tex
Changes; - More corrections made

\section{Research Question \ref{goal:complexity}}
Research Question \ref{goal:complexity}: \textit{``What is the time and computation complexity required to generate a ’similar’ keys for a targeted key pair?''} has been discussed by the project, the actual generation of keys was shown in Section \ref{sec:key_gen} where actual keys were generated. Further more the distribution of key permutations on a set of real-world keys were discussed in Section \ref{sec:averagePerms} and \ref{sec:vulnKeys}. To achieve this the tool GreenOnion was developed where inspiration was gathered from a currently available tool known as Scallion. Experimentation results were gathered and displayed in Section \ref{sec:SvG} that showed the significant increase in the number of near-collision keys GreenOnion can test for.

>>>>

\section{Research Question \ref{goal:complexity}}
Research Question \ref{goal:complexity}: \textit{``What are the time and computation complexity required to generate a ’similar’ keys for a targeted key pair?''} has been discussed by the project, the actual generation of keys was shown in Section \ref{sec:key_gen} where actual keys were generated. Further more the distribution of key permutations on a set of real-world keys were discussed in Section \ref{sec:averagePerms} and \ref{sec:vulnKeys}. To achieve this the tool GreenOnion was developed where inspiration was gathered from a currently available tool known as Scallion. Experimentation results were gathered and displayed in Section \ref{sec:SvG} that showed the significant increase in the number of near-collision keys GreenOnion can test for.
